\documentclass[10pt,letterpaper]{article}

\usepackage[ignoreheadfoot,top=1cm,bottom=1cm,left=2cm,right=2cm,footskip=1cm]{geometry}
\usepackage{titlesec}
\usepackage[dvipsnames]{xcolor}
\definecolor{primaryColor}{RGB}{0,0,0}
\usepackage{enumitem}
\usepackage[pdftitle={Curriculum},pdfauthor={Vicente Javier Viera Guízar},pdfcreator={LaTeX with RenderCV},colorlinks=true,urlcolor=primaryColor]{hyperref}
\usepackage{changepage}
\usepackage{paracol}
\usepackage{needspace}
\usepackage{iftex}

\ifPDFTeX
    \input{glyphtounicode}
    \pdfgentounicode=1
    \usepackage[T1]{fontenc}
    \usepackage[utf8]{inputenc}
    \usepackage{lmodern}
\fi

\usepackage{charter}

\raggedright
\AtBeginEnvironment{adjustwidth}{\partopsep0pt}
\pagestyle{empty}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}
\setlength{\topskip}{0pt}
\setlength{\columnsep}{0.15cm}
\pagenumbering{gobble}

\titleformat{\section}{\needspace{4\baselineskip}\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule]
\titlespacing{\section}{-1pt}{0.3cm}{0.2cm}

\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}

\newenvironment{onecolentry}{\begin{adjustwidth}{0.00001cm}{0.00001cm}}{\end{adjustwidth}}
\newenvironment{twocolentry}[2][]{\onecolentry\def\secondColumn{#2}\setcolumnwidth{\fill,4.5cm}\begin{paracol}{2}}{\switchcolumn\raggedleft\secondColumn\end{paracol}\endonecolentry}
\newenvironment{header}{\setlength{\topsep}{0pt}\par\kern\topsep\centering\linespread{1.5}}{\par\kern\topsep}

\let\hrefWithoutArrow\href

\begin{document}
\newcommand{\AND}{\unskip\cleaders\copy\ANDbox\hskip\wd\ANDbox\ignorespaces}
\newsavebox\ANDbox
\sbox\ANDbox{$|$}

\begin{header}
   \fontsize{25pt}{25pt}\selectfont Vicente Javier Viera Guízar

\vspace{4pt}

\fontsize{12pt}{12pt}\selectfont\itshape
Software Engineer

\vspace{5pt}

    \normalsize
    \mbox{México}%
    \kern5pt%
    \AND%
    \kern5pt%
    \mbox{\hrefWithoutArrow{mailto:vicentejvg@outlook.com}{vicentejvg@outlook.com}}%
    \kern5pt%
    \AND%
    \kern5pt%
    \mbox{\hrefWithoutArrow{tel:+52-331-178-29-95}{+52 33 1178 2995}}%
    \kern5pt%
    \AND%
    \kern5pt%
    \mbox{\hrefWithoutArrow{https://vicentejvg.netlify.app/}{Personal web page}}%
    \kern5pt%
    \AND%
    \kern5pt%
    \mbox{\hrefWithoutArrow{https://linkedin.com/in/vicentejvg}{linkedin.com/in/vicentejvg}}%
    \kern5pt%
    \AND%
    \kern5pt%
    \mbox{\hrefWithoutArrow{https://github.com/VicenteVieraG}{github.com/VicenteVieraG}}%
\end{header}

\vspace{\dimexpr5pt-0.3cm\relax}

\section{About Me}

\begin{onecolentry}
    Highly motivated Software Engineer with a strong foundation
    computer science. Passionate about developing innovative
    solutions and continuously improving my skills. Experienced in
    working on complex projects and committed to delivering high-quality results; excelling in dynamic,
    collaborative environments.
\end{onecolentry}

\section{Experience}

\begin{twocolentry}{Oct 2023 - Nov 2023}
    \textbf{Brainiac Web Research Intern} \textit{| Node.js, TypeScript, Three.js, GLSL}

    3D Brain zones activation interactive visualization.
    \begin{itemize}
        \item Loaded brain 3D model and brain connections from vertex arrays using \textbf{Node.js}.
        \item Added Interactivity to the visualization and lighting with \textbf{Three.js}.
        \item Implemented an approximation of a 3D Voronoi diagram algorithm to highlight activated brain's zones.

    \end{itemize}
    Exposed the results of a neuro-science research results on imagined speech.
\end{twocolentry}

\vspace{0.3cm}

\begin{twocolentry}{Feb 2023 - Oct 2023}
    \textbf{IBM PowerDash} \textit{| Nextjs, TypeScript, tRCP, Prisma, Tailwindcss, PowerShell}

    Web dashboard application development.
    \begin{itemize}
        \item Designed and implemented reusable core UI component library using \textbf{React} and \textbf{Tailwindcss}.
        \item Used \textbf{tRPC} to handle backend routes to fetch real-time data into UI components.
        \item Implemented a \textbf{SCRUM} methodology in the project development cycle.
    \end{itemize}

    Optimized team's certifications tracking and team creation.
\end{twocolentry}

\section{Education}

\begin{twocolentry}{Aug 2020 - Jun 2024}
    \textbf{Instituto Tecnológico de Estudios Superiores de Monterrey}, Bachelor of Science in Computer Science and Technology 
\end{twocolentry}

\begin{itemize}
    \item \textbf{GPA}: 92.83
    \item \textbf{Relevant Coursework}: Algorithms and data structures, Computer graphics, Linear algebra.
\end{itemize}

\section{Certifications}

\begin{itemize}[topsep=0pt,itemsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=*]
    \item \href{https://www.coursera.org/account/accomplishments/records/YRBFYOF8ZKB8}{Foundations of Coding Full-Stack} | Microsoft
    \item \href{https://www.coursera.org/account/accomplishments/verify/5C92VGE4SWFO}{Introduction to Programming With C\#} | Microsoft
    \item \href{https://api.badgr.io/public/assertions/MtqvVdKQSdmx8HospWE1aw}{Software Systems Developer} | \textit{Tecnológico de Monterrey}
    \item \href{https://api.badgr.io/public/assertions/EA0qVm6cRBykjIyOLQse7g}{Computational Infrastructure Implementation} | \textit{Tecnológico de Monterrey}
    \item \href{https://api.badgr.io/public/assertions/bE7-YqTpQM-ZdBLmjIq07Q}{Research Internship} | \textit{Tecnológico de Monterrey}
\end{itemize}

\section{Technologies}

\textbf{Languages}: C, C++, C\#, JavaScript, TypeScript, HTML, CSS, PowerShell.

\textbf{Frameworks}: Astro, Next.js, React, React Native, Svelte, Tailwind, SDL2, GLFW, OpenGL, .NET.

\textbf{Libraries}: Boost, ImGUI, glbinding.

\textbf{Developer Tools}: CMake, Make, minGW/MSVC/Clang LLVM, gdb, VCPKG, Git, GitHub, Visual Studio, Visual Studio Code, Figma

\section{Languages}
    Spanish(Native) | 
    English(C1/TOEFL ITP) | 
    French(Basic)

\end{document}

